---
title: "Locked down areas in Melbourne"
output:
  html_document:
    df_print: paged
---


```{r setup, echo=FALSE, include=FALSE}

#Postcode boundaries : ABS ASGS - Non ABS Structures

#Incorporates or developed using Administrative Boundaries ©PSMA Australia Limited licensed by the Commonwealth of Australia under Creative Commons Attribution 4.0 International licence (CC BY 4.0).
library(tidyverse)
library(spdplyr)
library(rgdal)
library(leaflet)
library(widgetframe)
library(knitr)
library(webshot)
if(!file.exists("POA_2016_AUST.shp")){
      download.file("https://www.abs.gov.au/ausstats/subscriber.nsf/log?openagent&1270055003_poa_2016_aust_shape.zip&1270.0.55.003&Data%20Cubes&4FB811FA48EECA7ACA25802C001432D0&0&July%202016&13.09.2016&Previous","postcodes.zip")
    unzip("postcodes.zip")
    file.remove("postcodes.zip")
}

postcode <- readOGR( 
  dsn="./" , 
  layer="POA_2016_AUST"
)

if(!file.exists("suburbs.json")){
        download.file("https://data.gov.au/geoserver/vic-suburb-locality-boundaries-psma-administrative-boundaries/wfs?request=GetFeature&typeName=ckan_af33dd8c_0534_4e18_9245_fc64440f742e&outputFormat=json","suburbs.json")
}

suburb <- readOGR("suburbs.json")

confined_melbourne <- tibble(POA_CODE16=c("3012", "3021", "3032", "3038", "3042", "3046", "3047", "3055", "3060","3064",
                                        "3031","3051"),
                             colour=c(rep("#ff8a00",10),
                                      rep("#ffdd00",2)))

zoo_lat <- -37.7841
zoo_lng <- 144.9515

fileName <- "Melbourne_Lockdown_20200630.html"
postTitle <-"Locked down areas in Melbourne - Test"

```



```{r echo=FALSE}


lockdown_areas <- postcode %>% left_join(confined_melbourne,by="POA_CODE16") %>%
                filter(!is.na(colour))


lockdown <- raster::intersect(suburb,lockdown_areas) %>%
            mutate(Suburb=paste(vic_loca_2,POA_CODE16,sep=" "))

#as.data.frame(lockdown_suburbs)
```


```{r echo=FALSE}

map<- leaflet(option=leafletOptions(zoomControl=TRUE)) %>%
  addTiles() %>%
  setView(lng=zoo_lng,lat=zoo_lat, zoom = 10) %>%
  addProviderTiles("OpenStreetMap.Mapnik") %>%
    addPolygons(data=lockdown,stroke = TRUE, smoothFactor = 0.3, fillOpacity = 0.8,fillColor=~colour,
                color="gray",opacity = 0.8,weight = 0.8,
              label=~Suburb) 

htmlwidgets::saveWidget(frameableWidget(map),'leaflet.html')
webshot("leaflet.html", file = "leaflet.png",
        cliprect = "viewport")
map

```


```{r out.height='30px'}
htmltools::includeHTML("https://www.carlosyanez.cl/wp-content/uploads/2020/07/leaflet.html")
```



From Wednesday midnight, 10 Melbourne [**postcode areas**](https://en.wikipedia.org/wiki/Postcodes_in_Australia) will enter lockdown, to contain the spread of covid-19. As per the [news report](https://www.abc.net.au/news/2020-06-30/victoria-coronavirus-hotspot-local-lockdowns-in-melbourne/12407138), the areas are **`r confined_melbourne`**. 

Although my postcode is not listed, it is in one of previously mentioned **hotspot** [LGAs](https://en.wikipedia.org/wiki/Local_government_in_Australia). So, to better understand which are exactly the places in lockdown, I put them in the below map.


To view the map in full screen, click [here](https://www.carlosyanez.cl/wp-content/uploads/2020/06/leaflet.html).

Postcode boundaries : [ABS ASGS – Non ABS Structures](https://www.abs.gov.au/AUSSTATS/abs@.nsf/DetailsPage/1270.0.55.003July%202016?OpenDocument)

Incorporates or developed using Administrative Boundaries ©PSMA Australia Limited licensed by the Commonwealth of Australia under Creative Commons Attribution 4.0 International licence (CC BY 4.0).

